\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-11 paper/main.tex
u

\usepackage{multirow}
\usepackage{xcolor}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

@@

\section{Related Work} 
Defects4J\cite{just2014defects4j}
BugsInPy~\cite{widyasari2020bugsinpy}
Tests4Py~\cite{smytzek2024tests4py}
Denchmark~\cite{kim2021denchmark}

>>>>

\usepackage{multirow}
\usepackage{xcolor}
\usepackage{xspace}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

@@

\section{Related Work} 
Several bug datasets have been proposed in literature for general software. Some
popular examples includes software-artifact infrastructure repository
(SIR)~\cite{do2005supporting} which was one of the bug datasets containing 81
artificial faults in projects across multiple languages,
Defects4J~\cite{just2014defects4j} which includes 357 real bugs across five
large real-world Java projects, BugsInPy~\cite{widyasari2020bugsinpy} containing
493 real bugs from 17 real-world Python programs, and
BugsJS~\cite{vancsics2020relationship} containing 453 bugs across 10 Javascript
projects.
%
Google's FuzzBench~\cite{metzman2021fuzzbench} provides an evaluation platform
for comparing general purpose fuzzers. Magma~\cite{hazimeh2020magma} is another
fuzzing benchmark built by \emph{front-porting} real bugs in latest version of
projects. In contrast to these general purpose benchmarks, \tname includes
reproducible bugs for Deep Learning libraries like PyTorch and TensorFlow, and
allows systematic benchmarking for DLL fuzzers.

% Defects4J\cite{just2014defects4j}
% BugsInPy~\cite{widyasari2020bugsinpy} Tests4Py~\cite{smytzek2024tests4py}
% Denchmark~\cite{kim2021denchmark}
